\documentclass[11pt,letterpaper]{article}

\usepackage[T1]{fontenc}
\usepackage{mathpazo}
\usepackage[margin=1in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\setstretch{1.05}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.9em}

\begin{document}

\hfill March 30, 2026

Dear Hiring Team,

I'm excited to apply for the Data Scientist role at Twitch. I'm graduating with my PhD in Information Systems Management at Carnegie Mellon, where my work focuses on empirical research, experimentation, causal inference, and how AI tools shape user behavior and workflows. I also bring a strong technical foundation from my engineering training and years of experience in Python, R, SQL, and large-scale data analysis.

In my PhD, I designed and ran a randomized study on how text-to-music AI tools affect ideation in music composition (140 in-person participants, 1,000+ online evaluators), including participant recruitment, survey design, interviews, and an AWS-hosted web app for data collection. I also collaborate with Spotify's Creator Economics team on causal research studying how platform features affect creator outcomes, and previously worked at Pandora designing A/B tests and building KPI dashboards for subscriber growth. During my time at Pandora, I also worked closely with the FP\&A team to maintain monthly active user forecast models and support recurring data sharing.

I am looking forward to the opportunity to meet with the team. Thank you for your consideration.

Sincerely,

Jose Eduardo Oros Chavarria \\
\href{mailto:joros@cmu.edu}{joros@cmu.edu} \\
(412) 500-4169 \\
\href{https://www.linkedin.com/in/joseoros}{linkedin.com/in/joseoros} \\
\href{https://sites.google.com/view/joseoros}{sites.google.com/view/joseoros}

\end{document}
