\documentclass[10pt,letterpaper]{article}

% Font
\usepackage[T1]{fontenc}
\usepackage{mathpazo}

% Page layout
\usepackage{geometry}
\geometry{top=0.68in, bottom=0.75in, left=0.78in, right=0.78in}

% Spacing
\usepackage{setspace}
\setstretch{1.04}
\usepackage{microtype}
\AtBeginDocument{\fontsize{10.5pt}{12.6pt}\selectfont}

% Colors
\usepackage[x11names]{xcolor}

% Page style
\pagestyle{empty}

% Section formatting
\usepackage{titlesec}
\titleformat*{\section}{\centering\LARGE\scshape}
\titleformat*{\subsection}{\bfseries\scshape\color{gray}}
\titlespacing*{\section}{0pt}{10pt}{5pt}
\titlespacing*{\subsection}{0pt}{6pt}{3pt}

% Lists
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.35em, label=\color{gray}{\textbullet}, nosep, topsep=2pt, itemsep=2pt}

% Links
\usepackage[hyphens]{url}
\urlstyle{same}
\usepackage[hidelinks, hypertexnames=false]{hyperref}

% Custom commands
\newcommand{\name}[1]{\section*{#1}}
\newcommand{\sep}{{\color{gray}\,\textbullet\,\,}}
\newcommand{\hsep}{\noindent\textcolor{gray}{\rule{\textwidth}{0.5pt}}}
\newcommand{\block}[1]{\begin{samepage}\hsep\subsection*{#1}\end{samepage}}

\begin{document}

\name{Jose Eduardo Oros Chavarria}

\begin{center}
(412) 500-4169 \sep \href{mailto:joros@cmu.edu}{joros@cmu.edu} \sep \href{https://www.linkedin.com/in/joseoros}{linkedin.com/in/joseoros} \sep \href{https://sites.google.com/view/joseoros}{sites.google.com/view/joseoros}
\end{center}

\block{Summary}

\noindent Data scientist with experience in empirical research, experimentation, causal inference, and AI evaluation. Previously supported subscriber growth and retention at Pandora and collaborated with Spotify on creator-economics research; current Carnegie Mellon work uses randomized experiments and proprietary platform data to study creator behavior, product value, and how AI-assisted tools change user outcomes.

\block{Skills}

\noindent\textbf{Programming:} SQL (PostgreSQL, BigQuery), Python (pandas, scikit-learn, statsmodels), R (fixest, ggplot2, tidyverse) \\
\textbf{Methods:} A/B Testing \& Experimentation, Causal Inference (Difference-in-Differences, Matching), Survey Design, GLMs, Survival Analysis, Machine Learning \\
\textbf{Tools \& Platforms:} Tableau, Airflow, AWS \\
\textbf{Domain:} Product Analytics, AI Evaluation, Creator Tools, Platform Economics

\block{Professional Experience}

\begin{itemize}[leftmargin=0pt, label={}]
\item \textbf{Carnegie Mellon University} \sep Doctoral Researcher \sep Pittsburgh, PA \hfill Aug 2019 -- present
  \begin{itemize}
  \item Led an end-to-end randomized experiment on generative AI ideation in music composition across 140 in-person participants and 1{,}000 online evaluators; found that melodies composed in the AI-assisted condition received lower perceived creativity ratings than the control group. Designed and deployed a web app on AWS, using LLM tools to help implement the system, to collect evaluation data for the study.
  \item Led a multi-year collaboration with Spotify's Creator Economics team, working with economists and data scientists to study how editorial playlisting affects artist engagement and off-platform outcomes for emerging artists. Used matching and difference-in-differences analysis on proprietary platform data.
  \item Studied whether early social media signals can predict commercial success for emerging recording artists by building classification models for major-label signing and Billboard-chart outcomes.
  \end{itemize}
\item \textbf{Spotify} \sep Economics Research Intern, Creator Economics \sep New York City, NY \hfill Summer 2022
  \begin{itemize}
  \item Analyzed how Spotify for Artists usage changes around touring to quantify product value to artists; conducted analysis in R on internal Spotify data, employing econometric tools including difference-in-differences, and presented results internally to economics and marketing stakeholders.
  \end{itemize}
\item \textbf{Pandora Media} \sep Data Analyst, Subscriber Growth \& Retention Insights \sep Oakland, CA \hfill Jan 2018 -- Aug 2019
  \begin{itemize}
  \item Supported lifecycle email and push campaigns for new and lapsed listeners by translating campaign criteria from the marketing team into SQL audience logic and treatment/control groups.
  \item Measured incremental campaign lift on listener reactivation, listening hours, and LTV using treatment-control comparisons.
  \item Maintained KPI tracking, dashboards, and MAU reporting and forecasting workflows; used Hive and Airflow to support recurring targeting datasets and Tableau to monitor campaign performance.
  \end{itemize}
\item \textbf{Pandora Media} \sep Marketing Analytics Science Intern \sep Oakland, CA \hfill Summer 2017
  \begin{itemize}
  \item Built a Python and SQL pipeline to log and process paid marketing engagement data for Pandora's marketing analytics team.
  \end{itemize}
\end{itemize}

\block{Selected Research}

\begin{itemize}[leftmargin=0pt, label={}]
\item \textbf{Help That Hurts: The Creativity Cost of Generative AI Ideation in Music Composition} \\
Randomized experiment combining participant and evaluator data to study how access to a text-to-music system changes ideation and perceived quality in human-composed music.
\item \textbf{Playlist-Induced Spillovers: Examining On- and Off-Platform Outcomes for Emerging Artists on Spotify} \\
Matched difference-in-differences study using Spotify's proprietary Playlist Pitching data to estimate effects on streams, engagement, and touring outcomes for emerging artists.
\end{itemize}

\block{Education}

\begin{itemize}[leftmargin=0pt, label={}]
\item \textbf{Carnegie Mellon University}, H.\ John Heinz III College \sep Pittsburgh, PA
  \begin{itemize}[label={}]
  \item Ph.D., Information Systems Management \hfill 2026 (expected)
  \item Daniel and Rise Nagin Dissertation Fellowship \hfill 2025
  \item Master of Information Systems Management, Business Intelligence and Data Analytics Track \hfill Dec 2017
  \end{itemize}
\item \textbf{Instituto Tecnol\'ogico Aut\'onomo de Mexico (ITAM)} \sep Mexico City, Mexico \hfill 2016
  \begin{itemize}[label={}]
  \item B.S., Telecommunications Engineering
  \item Baill\`eres Scholarship, full-tuition merit award for top admission exam score in Telecommunications Engineering
  \end{itemize}
\end{itemize}

\block{Additional Evidence}

\begin{itemize}[leftmargin=0pt, label={}]
\item \textbf{Teaching:} Recitation Instructor, Advanced Business Analytics, Carnegie Mellon University (2021 -- present). Led weekly sections for 35+ students on GLMs, survival models, and applied statistical modeling.
\item \textbf{Selected Presentations:} Spotify Tech Research Weekly, MIT BIG.AI, CODE@MIT, INFORMS Annual Meeting, Workshop on Information Systems and Economics.
\item \textbf{Languages:} English, Spanish (Native).
\end{itemize}

\end{document}
