\documentclass[10pt,letterpaper]{article}

% Font
\usepackage[T1]{fontenc}
\usepackage{mathpazo}

% Page layout
\usepackage{geometry}
\geometry{top=0.7in, bottom=0.75in, left=0.8in, right=0.8in}

% Spacing
\usepackage{setspace}
\setstretch{1.04}
\usepackage{microtype}

% Colors
\usepackage[x11names]{xcolor}

% Page style
\pagestyle{empty}

% Section formatting
\usepackage{titlesec}
\titleformat*{\section}{\centering\LARGE\scshape}
\titleformat*{\subsection}{\bfseries\scshape\color{gray}}
\titlespacing*{\section}{0pt}{10pt}{5pt}
\titlespacing*{\subsection}{0pt}{6pt}{3pt}

% Lists
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.35em, label=\color{gray}{\textbullet}, nosep, topsep=2pt, itemsep=2pt}

% Links
\usepackage[hyphens]{url}
\urlstyle{same}
\usepackage[hidelinks, hypertexnames=false]{hyperref}

% Custom commands
\newcommand{\name}[1]{\section*{#1}}
\newcommand{\sep}{{\color{gray}\,\textbullet\,\,}}
\newcommand{\hsep}{\noindent\textcolor{gray}{\rule{\textwidth}{0.5pt}}}
\newcommand{\block}[1]{\begin{samepage}\hsep\subsection*{#1}\end{samepage}}

\begin{document}

\name{Jose Eduardo Oros Chavarria}

\begin{center}
(412) 500-4169 \sep \href{mailto:joros@cmu.edu}{joros@cmu.edu} \sep \href{https://www.linkedin.com/in/joseoros}{linkedin.com/in/joseoros} \sep \href{https://sites.google.com/view/joseoros}{sites.google.com/view/joseoros}
\end{center}

\block{Summary}

\noindent Applied economist and data scientist with experience in experimentation, causal inference, retention, and platform analytics. Background includes subscriber growth work at Pandora, creator-platform research with Spotify, and current Carnegie Mellon research on digital markets and how generative AI changes creative work.

\block{Core Skills}

\noindent\textbf{Focus:} Product Analytics, Growth \& Retention, Platform Economics, AI Adoption \\
\textbf{Methods:} Experimentation, Causal Inference, Econometrics, Forecasting, GLMs, Survival Analysis \\
\textbf{Tools:} SQL, Python, R \\
\textbf{Languages:} English, Spanish (Native)

\block{Experience}

\begin{itemize}[leftmargin=0pt, label={}]
\item \textbf{Carnegie Mellon University} \sep Doctoral Researcher \sep Pittsburgh, PA \hfill Aug 2019 -- present
  \begin{itemize}
  \item Lead empirical research on digital platforms, creator markets, and generative AI using causal inference, experimentation, and large-scale observational analysis.
  \item Built a multi-year data-sharing collaboration with Spotify's Creator Economics team and designed studies on how platform promotion affects artist engagement and on- and off-platform outcomes.
  \item Translate ambiguous research and product questions into measurable frameworks and communicate findings to academic and industry audiences.
  \end{itemize}
\item \textbf{Spotify} \sep Economics Research Intern, Creator Economics \sep New York City, NY \hfill Summer 2022
  \begin{itemize}
  \item Conducted empirical analysis of artist performance and platform impact using proprietary Spotify data and causal inference methods.
  \end{itemize}
\item \textbf{Pandora Media} \sep Data Analyst, Subscriber Growth \& Retention Insights \sep Oakland, CA \hfill Jan 2018 -- Aug 2019
  \begin{itemize}
  \item Supported subscriber growth and retention decisions on the Marketing Analytics team by analyzing campaign performance and customer behavior.
  \item Ran experiments and developed forecasting models in R, Python, and SQL to measure incremental marketing impact and inform channel optimization.
  \item Built dashboards and reporting workflows to monitor subscriber KPIs and communicate results to cross-functional stakeholders.
  \end{itemize}
\item \textbf{Pandora Media} \sep Marketing Analytics Science Intern \sep Oakland, CA \hfill Jun 2017 -- Aug 2017
  \begin{itemize}
  \item Developed a Python and SQL pipeline for Pandora's paid marketing team to log and process digital advertising engagement data.
  \end{itemize}
\end{itemize}

\block{Selected Research}

\begin{itemize}[leftmargin=0pt, label={}]
\item \textbf{Playlist-Induced Spillovers: Examining On- and Off-Platform Outcomes for Emerging Artists on Spotify} \\
Studies how platform promotion affects creator growth and downstream outcomes using proprietary Spotify data and causal inference methods.
\item \textbf{Help That Hurts: The Creativity Cost of LLM Ideation in Music Composition} \\
Examines how generative AI tools change user behavior and output quality in creative work.
\end{itemize}

\block{Education}

\begin{itemize}[leftmargin=0pt, label={}]
\item \textbf{Carnegie Mellon University}, H.\ John Heinz III College \sep Pittsburgh, PA
  \begin{itemize}[label={}]
  \item Ph.D., Information Systems and Management \hfill 2026 (expected)
  \item Master of Information Systems Management \hfill Dec 2017
  \end{itemize}
\item \textbf{Instituto Tecnol\'ogico Aut\'onomo de Mexico (ITAM)} \sep Mexico City, Mexico \hfill 2016
  \begin{itemize}[label={}]
  \item B.S., Telecommunications Engineering
  \item Business Strategy Certification
  \end{itemize}
\end{itemize}

\block{Additional Evidence}

\begin{itemize}[leftmargin=0pt, label={}]
\item \textbf{Teaching:} Recitation Instructor, Advanced Business Analytics, Carnegie Mellon University (2021 -- present). Lead weekly sections for 10--20 graduate students on GLMs, survival models, and applied statistical modeling.
\item \textbf{Selected Presentations:} Spotify Tech Research Weekly (2025), INFORMS Annual Meeting (2025), Conference on Digital Experimentation @ MIT (2025), Workshop on Information Systems and Economics (2023).
\item \textbf{Honors:} Daniel and Rise Nagin Dissertation Fellowship (2025).
\end{itemize}

\end{document}
